\documentclass[11pt,letterpaper]{article}

\newcommand{\userName}{Artem Khomich}
\newcommand{\institution}{Concordia}
\usepackage{devdiary}

\begin{document}

\title{Development Diary}

\section*{Iteration I}

\subsection*{January 23}

After the my team created all the repositories and files for the project, as well as the roles were discussed:
\begin{itemize}
\item Setup Eclipse and all related software for development,
\item Downloaded the repo with a project code, written by Matthew,
\item Started reading the documentation for JAVAFX.
\end{itemize}

\subsection*{January 28}

Written classes for the Account, Account enity management (AccountDao), Account controller in analogue with existing Transaction classes. Made simple GUI testing for those.

\subsection*{February 2}
Rewritten controller, created different controllers for List of Accounts and Single. Encountered several bugs.


\subsection*{February 6}

Spent most of the day in parallel with work trying solve the errors with compiling my code. Installed Scene Builder and bunch of other software. Learned few tricks about case sensitivity of the JvaFX library and fxml documents. Merged code with a current code version.

\subsection*{February 28}

We had a class meeting at which roles were assigned. After ensuring the roles are assigned correctly we proceeded with the actual sub-tasks giving. After coders tasks were given the meeting was finished. I was satisfied with the way how it went.

\subsection*{March 7}

Today was the first DEMO. My team members weren't prepared 100\%, and additional requirements to the documentation were revealed, so we had to assign additional sub-tasks to documenters.

\subsection*{March 10}

Everything went smoothly for the team, people reported that their tasks are finished. There were only couple of people who didn't connect and inform of progress.

\subsection*{March 14}

Today is new DEMO. Before it happens I found my mistake in waiting too long for reply from one of the members and his work had to be urgently given to other team member. Despite that, DEMO will be ok.

\subsection*{March 21}

We held a meeting regarding last iteration roles. Was given a documenter role together with Mylene. Looking forward to do the testing for last documenting part.

\subsection*{March 27}

Had a meeting with Mylene, overviewd the exmple document, created new TEX template for our test cases.

\subsection*{April 3}

Filling the test documents with test case exmples.

\subsection*{April 5}

Having another team up with Mylene to continue on test cases. She is doing a lot of grammar checkup on my work.

\subsection*{April 6}

Did some extra tests for my part in it.1. Documented those.

\subsection*{April 8}

Checked with Mylene consistency of the document, pushed the changes on Github.

\end{document}