\iffalse 
https://tex.stackexchange.com/questions/287924/using-dates-as-section-numbering 
https://www.sharelatex.com/learn/Lists
\fi

\documentclass{article}
\usepackage[english]{babel}
\usepackage[calc,useregional,showdow]{datetime2}
\usepackage{titletoc}
\dottedcontents{section}[1.5in]{\bfseries\large}{1.5in}{10pt}

\usepackage{xparse}
\NewDocumentCommand{\datesec}{o m m}{%
	\renewcommand\thesection{\DTMdate{#2}}
	\IfNoValueTF{#1}
	{\section{#3}}
	{\section[#1]{#3}}
}

\title{Diary Entries}
\author{Matthew Ferderber}

\begin{document}
	\maketitle
	
	\datesec{2018-01-17}{Learning}
  \begin{itemize}
    \item Looked through the project description.
		\item Started looking through options for Desktop Java applications.
  \end{itemize}
  
	
	\datesec{2018-01-18}{Setup & Planning}
  \begin{itemize}
    \item Created the Github Repository.
    \item Created the initial commit.
    \item Chose structure for the application.
  \end{itemize}
  
  \datesec{2018-01-20}{User Requirement Planning & Research}
  \begin{itemize}
    \item Created several User Requirements based on the project description.
    \item Started learning tools for dependency management.
    \item Researched packages that would help with our project.
  \end{itemize}

  \datesec{2018-01-24}{Dependency Management}
  \begin{itemize}
    \item Decided on the tools that are required for the project.
    \item Began using Maven for dependency management.
    \item Chose JavaFX as the GUI library.
    \item Installed ORMLite and SQLite packages as dependencies under Maven.
  \end{itemize}

  \datesec{2018-01-24}{Transaction Use Case}
  \begin{itemize}
    \item Began working on Transaction use case.
    \item Seperated use case into model, views, and controllers.
    \item Implemented basic Data Access layer and Model.
  \end{itemize}

  \datesec{2018-01-25}{Unit Tests}
  \begin{itemize}
    \item Created sample unit tests to aid others in developing.
    \item Added unit tests for the Transaction model and data access.
  \end{itemize}
	
	\datesec{2018-01-25}{Documentation}
  \begin{itemize}
    \item Documented previously un-documented code.
  \end{itemize}
  
	\datesec{2018-01-30}{Transaction Use Case}
  \begin{itemize}
    \item Continued working on Transaction Use Case.
    \item Implemented various views for different Transaction uses (Detail, Edit, List).
	\end{itemize}
	
	\datesec{2018-02-06}{Transaction Use Case & Styling}
	\begin{itemize}
    \item Switched to VBox from FlowPane because of consistency issues.
    \item Worked on styling various components (CSS).
	\end{itemize}
	\datesec{2018-02-10}{GridPane}
	\begin{itemize}
    \item Switched all views to GridPane to align items better.
	\end{itemize}
	\datesec{2018-02-11}{Merged branches to master & Unit Tests}
	\begin{itemize}
    \item Merged all of the branches coders have been working on into Master before iteration 1 ends.
    \item Refactored code from different authors.
    \item Had trouble merging branches that contained conflicting code.
    \item Added dependency for TestFX to make unit testing JavaFX a lot easier.
  \end{itemize}
  \datesec{2018-03-3}{Reading Documentation & Start of Iteration 2}
  \begin{itemize}
    \item Read through the documentation to determine what needs to be done
    \item Decided which parts I would do.
  \end{itemize}
  \datesec{2018-03-04}{Architecture Description}
  \begin{itemize}
    \item Started working on the architecture description.
  \end{itemize}
  \datesec{2018-03-05}{Helped Teammate}
  \begin{itemize}
    \item Helped Eric figure out how to work with the ORMLite database adapter. Specifically, I helped him determine
    how to form a relation between two tables.
  \end{itemize}
  \datesec{2018-03-07}{Helped Teammate}
  \begin{itemize}
    \item Helped Max determine how to structure his statistics use case.
    \item Helped Viktoriya get the project running in Eclipse. She was having an issue with Eclipse not updating the
    project files once they've been changed. The solution was to right click and refresh the project in Eclipse.
  \end{itemize}

  \datesec{2018-03-13}{Worked on Architecture Diagram}
  \begin{itemize}
    \item Used StarUML to create the Architecture Diagram.
  \end{itemize}

  \datesec{2018-03-14}{Worked on MVC description}
  \begin{itemize}
    \item Wrote a description of MVC and how it fits in our project.
  \end{itemize}
  \datesec{2018-03-15}{Created MVC diagram}
  \begin{itemize}
    \item Created a diagram of MVC integration for our application in StarUML.
  \end{itemize}
  \datesec{2018-03-17}{Subsystem Interface Specifications}
  \begin{itemize}
    \item Wrote the subsystem specifications for Account.
    \item Began writing the Transaction subsystem specifications.
  \end{itemize}
  \datesec{2018-03-18}{Merging & Submission}
  \begin{itemize}
    \item Finished the Transaction subsystem specification.
    \item Communicated with team to merge documentation changes together.
    \item Submitted the final design documentation files.
  \end{itemize}


\end{document}