\iffalse 
https://tex.stackexchange.com/questions/287924/using-dates-as-section-numbering 
https://www.sharelatex.com/learn/Lists
\fi

\documentclass{article}
\usepackage[english]{babel}
\usepackage[calc,useregional,showdow]{datetime2}
\usepackage{titletoc}
\dottedcontents{section}[1.5in]{\bfseries\large}{1.5in}{10pt}

\usepackage{xparse}
\NewDocumentCommand{\datesec}{o m m}{%
	\renewcommand\thesection{\DTMdate{#2}}
	\IfNoValueTF{#1}
	{\section{#3}}
	{\section[#1]{#3}}
}

\title{Diary Entries}
\author{Maximilien Malderle}

\begin{document}
	\maketitle
	
	\datesec{2018-01-18}{Learning}
  \begin{itemize}
        \item Met the group for the first time, familiarized myself with the members.  
        \item Learned the members names and positions
        \item Looked through the project description.
		\item Started thinking on how to implement a business perspective to the project.
  \end{itemize}
  
	
	\datesec{2018-01-24}{Setup & Planning}
  \begin{itemize}
        \item Discussion related to the design of the application in the lab.
        \item Focused on the the layout of the application.
        \item Discussed possible features and use cases.
  \end{itemize}
  
  \datesec{2018-01-25}{Detailing of my specific tasks}
  \begin{itemize}
    \item Discussed the groups progress and inquired on possible helpful         tasks to work on.
    \item Switched from Organizer to Documentation role in the project.
    \item New task to focus on developing business goals.
  \end{itemize}

  \datesec{2018-01-31}{Progress Review}
  \begin{itemize}
    \item Wrote a BDC format business plan for the application.
    \item Discussed the totality of the project with the TA in the Lab.
    \item Decided that business goals should not be a complete business plan.
  \end{itemize}

  \datesec{2018-02-7}{Task Review}
  \begin{itemize}
    \item Familiarized myself with Latex to transcribe Diaries.
    \item Retooled the business plan to better fulfill the business goals format.
    \item Discussed the validity of the business goals.
  \end{itemize}

  
\end{document}
